Transferability of clinical prediction models for early trauma care

### 2019-06-24 ManuscriptMarkdown.Rmd

# Results
We analysed data from `r total.number.of.patients ` trauma patients to
investigate the effects of transfer on clinical prediction models (Table 1). The
total number of missing observations across all variables was `r
total.number.of.na ` in the entire study cohort. The sample with the highest
percentage of missing observations was the `r highest.percent.missing.name `
sample with `r highest.percent.missing.number `% incomplete observations. The
variable with the highest number of missing values was `r name.variable.na `,
with `r number.variable.na ` missing values, which constituted `r
round(percent.variable.na) `% of the total values for this variable. The
percentages of missing values for the other model predictors, GCS and SBP was `r
round(gcs.na$percentage)`% and `r round(sbp.na$percentage)`% respectively.

**Table 1. Sample characteristics of multiple imputed data.** Data is presented as medians with interquartile range (IQR) or counts with % as applicable.
```{r, echo = FALSE, results = "asis"} 
## Table 1
options(knitr.kable.NA = '')
kable(table_one_high_low, format = "markdown")
kable(table_one_metro_non_metro, format = "markdown")
kable(table_one_multi_single, format = "markdown")
``` 
Abbreviations: GCS glasgow coma scale, SBP systolic blood pressure, RR respiratory rate, ISS injury severity score, NISS new injury severity score

>>>>

# Results
We analysed data from `r total.number.of.patients ` trauma patients to
investigate the effects of transfer on clinical prediction models (Table 1). The
total number of missing observations across all variables was `r total.number.of.na ` 
in the entire study cohort. The sample with the highest
percentage of missing observations was the `r highest.percent.missing.name `
sample with `r highest.percent.missing.number `% incomplete observations. The
variable with the highest number of missing values was `r name.variable.na `,
with `r number.variable.na ` missing values, which constituted `r round(percent.variable.na) `
% of the total values for this variable. The percentages 
of missing values for the other model predictors, GCS and SBP was `r round(gcs.na$percentage)`
% and `r round(sbp.na$percentage)`% respectively.

**Table 1. Sample characteristics of multiple imputed data.** Data is presented as medians with interquartile range (IQR) or counts with % as applicable.
```{r, echo = FALSE, results = "asis"} 
## Table 1
options(knitr.kable.NA = '')
# kable(results$table.one.list$Characteristics_table_of_high.volume.vs.low.volume , format = "markdown")
# kable(results$table.one.list$Characteristics_table_of_metropolitan.vs.non.metropolitan , format = "markdown")
# kable(results$table.one.list$Characteristics_table_of_multi.centre.vs.single.centre , format = "markdown")

kable(table_one_high_low, format = "markdown")
kable(table_one_metro_non_metro, format = "markdown")
kable(table_one_multi_single, format = "markdown")
``` 
Abbreviations: GCS glasgow coma scale, SBP systolic blood pressure, RR respiratory rate, ISS injury severity score, NISS new injury severity score
